Constraining gravitational wave amplitude birefringence with GWTC-3

### 2023-02-11 src/tex/ms.tex
Better naming

Since birefringence impacts the observed amplitude ratio of left- and right-handed modes, it could also affect inferences about the source inclination \cite{Alexander:2009tp}.
However, the two effects are degenerate only if the frequency dependence of Eq.~\eqref{eq:waveform_modification} is neglected.
This is easy to see from Eq.~\eqref{eq:waveform_modification}, since the implied polarization ratio for the $\ell = |m| = 2$ mode of a nonprecessing source is
\begin{equation}
    \frac{h_{L}^\mathrm{br}}{h_{R}^\mathrm{br}}=\left(\frac{1-\cos\iota}{1+\cos\iota}\right)^2
    \exp\left({2\kappa\frac{d_C}{1\, \mathrm{Gpc}}\frac{f}{100\, \mathrm{Hz}}}\right)\, .
    \label{eq:modified_amplitude_ratio}
\end{equation}
For an isolated Fourier mode of definite frequency $f$, the effect of birefringence will be degenerate with a change in inclination; however, if multiple modes come into play, then no change in inclination can mask the effect of birefringence, which will generate dephasing in the time domain waveform (Fig~\ref{fig:birefringence_frequency_domain}).

\begin{figure}
    \script{birefringence_frequency_domain.py}
    \includegraphics[width=\columnwidth]{figures/birefringence_frequency_domain.pdf}
    \caption{
        The observed Fourier amplitude of two polarizations of a simulated GW signal with and without birefringence.
        The amplitudes, as GR predicts, are shown in dotted lines with blue and orange colors representing the left-handed and right-handed polarizations.
        The amplitudes with birefringence are shown in solid lines with blue and orange colors representing the left-handed and right-handed polarizations.
        This plot shows the effect of amplitude birefringence with frequency dependence.
        \mi{@Thomas can you add a panel with the time-domain waveforms (maybe just for L or R)?}
    }
    \label{fig:birefringence_frequency_domain}
\end{figure}

@@

\section{Illustration of birefringence}
\label{sec:time_domain}

\begin{figure}[h]
    \script{birefringence_time_domain.py}
    \includegraphics[width=\columnwidth]{figures/birefringence_time_domain.pdf}
    \caption{The observed time domain signal with and without birefringence.}
    \label{fig:birefringence_time_domain}
\end{figure}

>>>>

Since birefringence impacts the observed amplitude ratio of left- and right-handed modes, it could also affect inferences about the source inclination \cite{Alexander:2009tp}.
However, the two effects are degenerate only if the frequency dependence of Eq.~\eqref{eq:waveform_modification} is neglected.
This is easy to see from Eq.~\eqref{eq:waveform_modification}, since the implied polarization ratio for the $\ell = |m| = 2$ mode of a nonprecessing source is
\begin{equation}
    \frac{h_{L}^\mathrm{br}}{h_{R}^\mathrm{br}}=\left(\frac{1-\cos\iota}{1+\cos\iota}\right)^2
    \exp\left({2\kappa\frac{d_C}{1\, \mathrm{Gpc}}\frac{f}{100\, \mathrm{Hz}}}\right)\, .
    \label{eq:modified_amplitude_ratio}
\end{equation}
For an isolated Fourier mode of definite frequency $f$, the effect of birefringence will be degenerate with a change in inclination; however, if multiple modes come into play, then no change in inclination can mask the effect of birefringence, which will generate dephasing in the time domain waveform (Fig~\ref{fig:birefringence}).

\begin{figure}
    \script{birefringence.py}
    \includegraphics[width=\columnwidth]{figures/birefringence.pdf}
    \caption{
        The observed Fourier amplitude of two polarizations of a simulated GW signal with and without birefringence.
        The amplitudes, as GR predicts, are shown in dotted lines with blue and orange colors representing the left-handed and right-handed polarizations.
        The amplitudes with birefringence are shown in solid lines with blue and orange colors representing the left-handed and right-handed polarizations.
        This plot shows the effect of amplitude birefringence with frequency dependence.
        \mi{@Thomas can you add a panel with the time-domain waveforms (maybe just for L or R)?}
    }
    \label{fig:birefringence}
\end{figure}

@@

\section{Illustration of birefringence}
\label{sec:birefringence_appendix}

\begin{figure}[h]
    \script{birefringence_appendix.py}
    \includegraphics[width=\columnwidth]{figures/birefringence_appendix.pdf}
    \caption{The observed time domain signal with and without birefringence.}
    \label{fig:birefringence_appendix}
\end{figure}
